Suplementary Material 3: Run Simulations on the Last Birth Omited Data

### 2023-04-05 S3_run_simulations_EE_not_last.Rmd
remove clutter

## Data Import 9 Other European Populations

```{r}
##Import and pre-proccess twinR package data

## Filter the raw data to only keep data with monthly resolution:
data_births_monthly <- twinR::filter_data(twinR::data_births_all)

data_births_monthly <- add_last_birth(data_births_monthly)
data_births_monthly_not_last <- data_births_monthly[!data_births_monthly$last,]

@@

>>>>

@@

#remove unnecessary data frames
rm(data_births_monthly_EE, data_births_monthly_EE_not_last)
